MCTS Based on Simple Regret

### 2012-04-04 paper/srcr/paper.tex
current state

The pseudocode of this two-stage rollout for an undiscounted MDP is in
Algorithm~\ref{alg:two-stage-mcts}: \textsc{FirstAction} selects the first
step of a layout (line~\ref{alg:srcr-first-action}), and
\textsc{NextAction} (line~\ref{alg:srcr-next-action}) selects steps during
the rest of the layout (usually using UCB). The reward statistic for
the selected action is updated (line~\ref{alg:srcr-update-stat}), and
the sample reward is back-propagated (line~\ref{alg:return-reward}) 
towards the current root.

>>>>

The pseudocode of this two-stage rollout for an undiscounted MDP is in
Algorithm~\ref{alg:two-stage-mcts}: \textsc{FirstAction} selects the first
step of a rollout (line~\ref{alg:srcr-first-action}), and
\textsc{NextAction} (line~\ref{alg:srcr-next-action}) selects steps during
the rest of the rollout (usually using UCB). The reward statistic for
the selected action is updated (line~\ref{alg:srcr-update-stat}), and
the sample reward is back-propagated (line~\ref{alg:return-reward}) 
towards the current root.
